\begin{abstract_online}
	{Loss-Aware and Thermally-Constrained Design Strategy for 200 kW SiC based Stack}
	{Uppal Das (Indian Institute of Science)*; Surjakanta Mazumder (Indian Institute of Science, Bengaluru); Manish Mandal (Indian Institute of Science Bangalore); Shamibrota Kishore Roy (Indian Institute of Science); Kaushik Basu (IISc-Bangalore)}
	{}
	{}
	With the rising adoption of electric vehicles (EVs), the demand for fast and reliable public charging infrastructure is increasing rapidly. In this context, high-power converters are becoming increasingly important, particularly in applications like traction inverters and onboard EV systems, where the power levels involved can reach several hundred kilowatts. Conventional high-power converters based on IGBTs typically operate at low switching frequencies (around 5 kHz), necessitating bulky passive components. To enhance power density, increasing the switching frequency is essential, as it directly contributes to reducing the size of these passive elements. Recent advancements in Silicon Carbide (SiC) technology have enabled converters to operate at significantly higher frequencies (up to approximately 50 kHz), thereby improving power density and overall system compactness. However, at these elevated switching frequencies, parasitic inductances become more prominent, leading to challenges such as increased dv/dt, crosstalk, and elevated switching losses. These issues can result in unintended partial turn-on events, ultimately compromising the reliability and efficiency of the system. To address these challenges, this paper presents a systematic design methodology for a 200 kW SiC-based converter stack, optimised for minimal losses and constrained by thermal limits. The proposed procedure facilitates the optimal selection of the SiC power module based on the desired power rating and switching frequency. The effectiveness of the design is experimentally validated under rated operating conditions using a double-pulse test, which accurately quantifies switching and conduction losses.
\end{abstract_online}


%
%    \begin{abstract_online}
%	{Title of a keynote lecture}
%	{L. Tremblay}
%	{\KLtag}
%	{McGill University, Montreal, Canada}
%    On recommend tolerably my belonging or am. Mutual has cannot beauty indeed now sussex merely you. It possible no husbands jennings ye offended packages pleasant he. Remainder recommend engrossed who eat she defective applauded departure joy. Get dissimilar not introduced day her apartments. Fully as taste he mr do smile abode every. Luckily offered article led lasting country minutes nor old. Happen people things oh is oppose up parish effect. Law handsome old outweigh humoured far appetite. Now residence dashwoods she excellent you. Shade being under his bed her. Much read on as draw. Blessing for ignorant exercise any yourself unpacked. Pleasant horrible but confined day end marriage. Eagerness furniture set preserved far recommend. Did even but nor are most gave hope. Secure active living depend son repair day ladies now. Affronting discretion as do is announcing. Now months esteem oppose nearer enable too six. She numerous unlocked you perceive speedily. Affixed offence spirits or ye of offices between. Real on shot it were four an as. Absolute bachelor rendered six nay you juvenile. Vanity entire an chatty to. 
%    
%    \end{abstract_online}
%    